---
title: "rsaga terrain basic"
output: html_document
date: "2023-02-24"
---

# Overview
This script now runs three parts of the process. 

1. Basic Terrain metrics
2. SAGA Gird format to ASCii format
3. ASCii format to Geotiff

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Calculate Basic Terrain Metrics
```{r}
rm(list=ls()) ### (you may not want this line) clear workspace   CAUTION!!!
```



# Packages
```{r}
library(RSAGA)
library(gdalUtilities)
library(terra)
library(sf)
```


# Rsaga 
This RSAGA version has been tested with SAGA GIS versions between 2.3.1 and 8.4.1.
```{r}
rsaga.path <- "C:/Users/atalucci/Documents/Programs/saga-8.5.1_x64"
```

```{r}
env <- rsaga.env(path=rsaga.path) 
```



# Aspect Slope Curvature
```{r}
rsaga.slope.asp.curv(in.dem="../data/dems/FABDEM_EA_YK.asc", 
out.aspect = "../outputs/aspect_EA_YK",
out.slope = "../outputs/slope_EA_YK",
out.cprof = "../outputs/cprof_EA_YK",
out.cplan = "../outputs/cplan_EA_YK",
method = "poly2zevenbergen",
unit.slope = "radians",
unit.aspect = "degrees",
env = env)
```
# 2. Saga Grid to ASCII
```{r}
rm(list=ls()) ### (you may not want this line) clear workspace   CAUTION!!!
```




## Packages
```{r}
library(RSAGA)
library(gdalUtilities)
library(terra)
library(sf)
```

```{r}
rsaga.path <- "C:/Users/atalucci/Documents/Programs/saga-8.5.1_x64"
```

```{r}
env <- rsaga.env(path=rsaga.path) 
```



## Slope
```{r}
rsaga.sgrd.to.esri(in.sgrds = "../outputs/slope_EA_YK", out.grids = "../outputs/slope_EA_YK", format = "ascii", env = env)
```

## cprof
```{r}
rsaga.sgrd.to.esri(in.sgrds = "../outputs/cprof_EA_YK", out.grids = "../outputs/cprof_EA_YK", format = "ascii", env = env)
```

## cplan
```{r}
rsaga.sgrd.to.esri(in.sgrds =  "../outputs/cplan_EA_YK", out.grids = "../outputs/cplan_EA_YK", format = "ascii", env = env)
```

# aspect
```{r}
rsaga.sgrd.to.esri(in.sgrds =  "../outputs/aspect_EA_YK", out.grids = "../outputs/aspect_EA_YK", format = "ascii", env = env)
```


# 3.Ascii to Geotiff
```{r}
rm(list=ls()) ### (you may not want this line) clear workspace   CAUTION!!!
```




## Packages
```{r}
library(RSAGA)
library(gdalUtilities)
library(terra)
library(sf)
```

```{r}
rsaga.path <- "C:/Users/atalucci/Documents/Programs/saga-8.5.1_x64"
```

```{r}
env <- rsaga.env(path=rsaga.path) 
```

### Aspect
```{r}
aspect<-rast("../outputs/aspect_EA_YK.asc")
```


```{r}
writeRaster(aspect, filename="../outputs/aspect_EA_YK.tif", filetype = "GTiff", overwrite=TRUE)
```

### Slope
```{r}
slope<-rast("../outputs/slope_EA_YK.asc")
```

```{r}
writeRaster(slope, filename="../outputs/slope_EA_YK.tif", filetype = "GTiff", overwrite=TRUE)
```

### cprof
```{r}
cprof<-rast("../outputs/cprof_EA_YK.asc")
```

```{r}
writeRaster(cprof, filename="../outputs/cprof_EA_YK.tif", filetype = "GTiff", overwrite=TRUE)
```

### cplan
```{r}
cplan<-rast("../outputs/cplan_EA_YK.asc")
```


```{r}
writeRaster(cplan, filename="../outputs/cplan_EA_YK.tif", filetype = "GTiff", overwrite=TRUE)
```



*****************************************************
# Additional curvature measures
```{r eval=FALSE, include=FALSE}
rsaga.slope.asp.curv(in.dem="../data/dems/DEMEA1NWT2014.asc", 
                     out.cgene = "../outputs/cgene",
                     out.ctang = "../outputs/ctang",
                     out.clong = "../outputs/clong",
                     out.ccros = "../outputs/ccros",
                     method = "poly2zevenbergen",
                     env = env)
```


```{r eval=FALSE, include=FALSE}
rsaga.slope.asp.curv(in.dem="../data/dems/DEMEA1NWT2014.asc", 
                     out.cmini = "../outputs/cmini",
                     out.cmaxi = "../outputs/cmaxi",
                     out.ctota = "../outputs/ctota",
                     out.croto = "../outputs/croto",
                     method = "poly2zevenbergen",
                     env = env)
```

